Paris by night is a sight unlike any other. The pearl of the Seine is alive with the flicker of the gaslights along its big streets like the Champs-Elys\'{e}es. Golden hued veins that turn Paris from just a city into something more the pulsing throbbing heart of a libertarian society. Where the good people may walk the streets at night ins afety and engage in pleasantries. So very much unlike the miserable heart of the Commonwealth, London, with its gray streets and gray weather and constant rain. Here in this city of Gas, Light, and Steam is where the true future of humanity lies. At least that is what they want you to believe. Like everything even Paris has two sides and the more brilliant one side is the darker and edgier the other usually is. Here deep in the side streets of PAris' old quarters there wasn't much to see of the shining new future. the gaslights were flaky at best and the houses not connected to the cities pipe heating system smelled of biting smoke from the wood stoves. But here people at least could afford a homewithout being a rich merchant and here one could still places like the Coq d'Or, a seedy tavern with cheap women and even cheaper wine, where one could have peace from the games of the gentry. Or so I had thought\dots

\newscene

You didn't had to look up as she entered the tavern, you just knew it. Her presences filled the smoky tavern and the sudden silence filled the room as the patrons regarded her. I emptied the last dregs of a bottle of cheap red and regarded her fine silk dress as she made her way over to my table. People parting in front of her like waves in front of a ship. The clockwork pendant hanging from her neck marked heras an artisans apprentice, but a very rich artisan as it seemed. "Commisaire Renard?" Her eyes rested with thinly veiled contempt on my unshaven face. "Not anymore." I muttered "that rank is a thing of the past my young lady. What brings you to this arse end of the town? I somehow doubt you are here for the company?" She regarded me coldly as if she was trying to reach a decision and then suddenly sat down and picked up the empty bottle. With a sigh she discarded it and waved the barman to bring another. "No I am indeed not here for your\dots charming\dots company. But I need help and a little bird told me you would be the one I wanted." Mustering me again she added to herself "Although I am beginning to doubt that bird." The barman arrived with another battle and two cleanest glasses I had seen in this tavern so far. She waved him away. "A bird by the name of\dots?" I asked. She hesitated a moment and then told me "Laroche." "My old partner." I acknowledged and sighed. "Did he tell you to bring me back to the path of good and righteousness?" "No, he said you were a bastard. A drunk cynical bastartd. But if i would need someone with a brain that would work for money you'd be the best there is." Laughign I took another swig of wine and regarded her a bit mor ecuriously "You know he just might be right for a change. But I guess you are asking yourself if this drunk still has any kind of brains left. Well let me tell you even half drunk I have more wits than those fools at the gendarmerie together." A sardonic smile crossed her face aas she sneered "Then how is it that the comissaire Laroche is parading around in a nice uniform while you waste your time drinking" she looked around "and probably whoring away your last franc?" "It's because brains aren't in high demand in this world andn either is the truth over some facts my little dove.  And don't you worry about my life, since my old 'friends' throw some scrabs" I looked at her "my way now and then I manage. So tell me what happend? Some scary thief pinched some gems from you? Need me to point you to the nearest fence where you can buy them back?" Anger flared in her eyes but she didn't explode at my jib as I expected. Instead the anger was held in check with iron determination as she slowly and pointedly spoke out "It's not thievery comissaire. It is murder."

\newscene

Those words hit me like bucket of cold water and sobered me up. My eye searched her face, rally looking at her for the first time. The tale was all there for those who knew how to see. The outrage carefully hidden under an icy layer of control, the way her jawline clenched when she said the words and the deep sadness that replaced her eyes. This woman lost someone close to her and she was far from over it. I placed my glass carfeully in front of me. "What happened?" She took a deep breath "La rue St. Germaine happened." "The watch accident?" Her eyes flared and her hand slapped on the table "It wasn't an accident! No normal watch could have malfunctioned like this." "The boy? the one who was killed, he mant a lot do you didn't he?" "He\dots George\dots he was just a messenger boy, but he was a decent man. We were engaged." A tear appeared in her eye and she cleared it away with her hand. "This simply shouldn't have happened." Watching her I sighed "What makes you so sure it was murder? Did he have money troubles? Was he threatend in any way? And why doesn't the gendarmerie investigate if there is doubt?" "The gendarmerie?" she snorted "those cretins wouldn't know a spring from a coq, much less of how they fit together in a watch but for me it is second nature. I am an artisan clockwork and springs are my lifeblood and there is no way a malfunctioned watch could wind up that much tension and\dots" "And still keep the time accurately." I finished hThose words hit me like bucket of cold water and sobered me up. My eye searched her face, rally looking at her for the first time. The tale was all there for those who knew how to see. The outrage carefully hidden under an icy layer of control, the way her jawline clenched when she said the words and the deep sadness that replaced her eyes. This woman lost someone close to her and she was far from over it. I placed my glass carfeully in front of me. "What happened?" She took a deep breath "La rue St. Germaine happened." "The watch accident?" Her eyes flared and her hand slapped on the table "It wasn't an accident! No normal watch could have malfunctioned like this." "The boy? the one who was killed, he mant a lot do you didn't he?" "He\dots George\dots he was just a messenger boy, but he was a decent man. We were engaged." A tear appeared in her eye and she cleared it away with her hand. "This simply shouldn't have happened." Watchier sentence. She gave me a baffled look and then nodded. "The watch was important for his work. He did a lot of timed deliveries and some merchants only keep certain hours for messages and he was one of the most reliable messenger." she explained. "And since he was good at his job and since his fiancee was an artisan he couldn't do with an inaccurate watch" I reasoned. "So it is a mistery but why me? there are lots of other investigators in this town\dots" I asked. "Lots of fools who will tell me what they think I want to hear but I don't need kind words. I need answers and the truth" she stared at her hands "If it really was an accident I need to know and if it wasn't as I suspect I need to know why and who so thatwhoever is responsible gets what he deservers." she said with the tension of a steel spring winding up in that last sentence. "Laroche told me tht you are the best there is and that while you will take my money you won't be bought. That you will tell the truth no matter what I want to hear. That you are ' the french who can't be bought'." I snickered "Oh I can be bought but noone could afford the price till now." Misunderstanding she threw a bag of coins on the table. "This are all of our savings for our wedding. Take it but bring me those answers. " she glared.My hands waved soothingly "That is not what I meant but I 'm still not convinced that it was anything else than an accident. But you got me intrigued. I will look into it and ask a few old friends. Maybe even Laroche and then we will talk again." She gave me a long calculating look and then nodded. "You will find me at the artisans school. My name is Angelique." then she stood up and left the tavern leaving the bag of coins on the table.
er sentence. She gave me a baffled look and then nodded. "The watch was important for his work. He did a lot of timed deliveries and some merchants only keep certain hours for messages and he was one of the most reliable messenger." she explained. "And since he was good at his job and since his fiancee was an artisan he couldn't do with an inaccurate watch" I reasoned. "So it is a mistery but why me? there are lots of other investigators in this town\dots" I asked. "Lots of fools who will tell me what they think I want to hear but I don't need kind words. I need answers and the truth" she stared at her hands "If it really was an accident I need to know and if it wasn't as I suspect I need to know why and who so thatwhoever is responsible gets what he deservers." she said with the tension of a steel spring winding up in that last sentence. "Laroche told me tht you are the best there is and that while you will take my money you won't be bought. That you will tell the truth no matter what I want to hear. That you are ' the french who can't be bought'." I snickered "Oh I can be bought but noone could afford the price till now." Misunderstanding she threw a bag of coins on the table. "This are all of our savings for our wedding. Take it but bring me those answers. " she glared.My hands waved soothingly "That is not what I meant but I 'm still not convinced that it was anything else than an accident. But you got me intrigued. I will look into it and ask a few old friends. Maybe even Laroche and then we will talk again." She gave me a long calculating look and then nodded. "You will find me at the artisans school. My name is Angelique." then she stood up and left the tavern leaving the bag of coins on the table.

\newscene

Coming Home is always a strange feeling but especially for me. Home is not the place where my bed stands and where I go to sleep. At least not for me. I had been one of those gendarmes that were married to their job. So coming back to the old gothic style building with its high arches and the brass pneumatic delivery tubes that gave it the resemblance of a heart beating with the pulse of information evoked a lot of old memories in me. Bitter memories were the freshest so I avoided the high arched front doors with their reception area and wandered around to the back. Noone was in sight which was good. I slendered over to the fire exits. Smoking was prohibitied in the building when i worked there and I assumed it was still. But most smokers creatures of habit as they were couldn't go a whole day without one. One of them eventually found out how to open a fire exit without tripping the alarm. Which wasn't that hard from the inside, but after a smoker locked himself out a few times and got a scolding from his superiors they learned another trick. I started rattling at the dors and smiled as the second one popped open. Namely how to fix the lock so that they couldn't get themselves locked out anymore. Fools. I didn't bother with makeup or anything which might wonder someone who didnt work in a big ministry before. Most ministries are like an anthill, there are a lot of checks to make sure only the right people get in but once you are in everyone just assumes you are one of the good ones. And like most anthills there were too many people for anyone to know each face so just striding down the hallway like you were allowed to be there and not look anyone in the face when you could help it was the best cover you could hope for. That I knew exactly where I was going helped a lot of course. I turned the corner of a long hallway and stood in front of a little used stairway in a sidewing. I followed the steps downwards till the wood paneled walls gave way to floored walls telling me I reached the level of the morgue. I made my way to the room of records where the reports of the autpsies were being held. I pushed open the door and stared on a table with a teapot and two teacups and a collection of biscuits. "Come in come in\dots" the old doc Smith beckoned. "Laroche mentioned that I might have a visitor soon, so I hope you don't mind if I prepared some tea." Astonished I entered the room and closed the door behind me. "So the sly bastard reckoned I'd take his bait and come here?" I asked Smith. "Well he might have been inclined to send the yound lady on her way if I didnt voiced some suspisions as well." I raises my eyebrows. The doc took his brassrimmed spectacles of and started to methodically clean them and I sighed impatiently. He placed them onhis nose again and continued "Well you see I am a man of science, but of the science of the human body not of clockwork. But for all that I know the damage that poor boy suffered shouldn't have been that extensive. That much force requires high grade springs whereas that type of accident is normally best explained by low grade materials." He looked at me and nodded satisfied that I wasn't surprised. And I think we all know your interest in a difficult mistery is seemingly the only thing that nowadays manages to draw you away from the bottle and to a cup of tea with an old friend." He reached for the teapot and poured each of us a cup "Somethign that happens far to seldom and under much too unhappy circumstances for my tastes these days." He added. A smirk stole on my lips "You always had a curious way of sending a message my friend. But strange as your ways are they seem to work, you got me into this game, so waht can you tell me about this mistery besides that it was an impossible clock?"Carefully picking up the fine china I took a sip. English black tea with just a hint of lemon. "Well as you understand I can't give information about an open case to someone outside. Even if that someone was a valued member of the gendarmerie like yourself. So I can't tell you that we have young victime maybe 20years old. healthy apart from that hole in his chest. And of course you aren't to know that he hasn't had any trouble with the law so far, a clean record, not even a reprimand for gambling so that debts are at least unlikely." "Besides debtors rather tend to break a few bones than to kill. Death makes paying off kind of hard." I interjected "Yes yes of course. What I meant non of the usual directions seem to lead somewhere. Of course if you had access to the file" he pointed to a vanilla envelope on a table " you might make your own enquiries with the relatives coworkers etc. Now If i just could remember whree I put the file, I'm getting kind of forgetful on my old days you see? I'm sure I have it somewhere around here sicne noone could have taken it, since we all know only people who are allowed here come this far into the building." he winked "maybe i left it in my upstairs office, I think I might go and check there now."
