The sun shone bright and clear over the village as I packed the last items in the basket for the weekly supply run to the foreigners base. I brushed my long blonde hair aside and smiled as I thought of them. They arrived a week ago in their glorious airship and they descended like angels from the heaven. Of course I had heard of airships and the great steam machines of the empire, I wasn't a backwater or something, but actually seeing one! As it turned out the foreigners were a science party from the University of Edinburough who came to explore the mistery of this tempered island amidst the cold sea of ice and they were a dull bunch indeed. Except John. John the youngest of them, the one who wasn't an old geezer. The one i would see again in just a short while\dots

\newscene

Father called from behind the counter of the Inn for me to be careful and back before sunset but i just waved him off and shouldered the backpack and went on my way. It's a mild day as I head with the foreigners scheduled supplies out towards the village exit where the road leads to the islands centre and the black basalt obelisks that ring our village loom up before me. I touch one of them for good luck as I always do and then laugh at the superstition. As if stones could bring luck. John with his scientific wisdom would probably scold me for being so foolish and guiltily I place my hand on the tiny piece of black stone hanging from my neck. "I would not be too quick to discard the old ways, young One" rasps a voice behind me. Startled i turn around to see the villages hag giving me an amused smile. "I.. I..." I stammer as my cheeks redden. She chuckles and continues "These men who think they have all the answers\dots There is more in heaven and earth than they can explain, more than they bargained for. These stones were here before them and they will protect us after they are long gone.But i guess at your age you are probably more interested in that young fellow" she chuckles again and waves me off. "Well go on then it's about time you sought yourself a man." Embarassed by her I turned away with reddened cheeks and stormed along the path along the green meadows and boulders that were strewn among them.

"Stupid old hag." I curse as soon as I am a safe distance from the village, what does she know of love and continue along the path and soon enough I leave the grass plains behind me and start to climb into the hills. Up here the winds are swifter and bite harder and I start to shiver. It's not far now, the scientists have their base camp at the foot of 'old Firespitter' the old volcano that dominates this part of the island and I thank the spirits that old Spitter isn't in a foul mood and that the air only slightly smells like rotten eggs.

\newscene

I arrive at the base camp only to find it deserted. I stomp my foot on the ground. "So much for hoping to find a galant gentlemen here waiting for me to shower me with compliments" I grumble as I put the backpack on the ground and start to look around for someone. "Hello? John? Professor?\dots" I call out as I wander around the deserted camp but there does not seem to be anyone around. The only thing I find is a small path that leads towards old Firespitter and seems to vanish in his flank. The rocky flanks are strewn with black stones and the path goes around a big boulder and ends in a cavern opening. My heart was pounding loudly in my chest as I peeked into the darkness. I couldn't see anything! But wait where this footsteps that where echoing along? Carefully I inched into the cave and went silenty stepped towards the first bend as massive black somethign darted around it. I screamed as his big black head with big round glassy eyes shot towards my face. I tried to get away and took a step back as it collided with me my head banging hard against the stone wall and I went to the flooor in deep dark oblivion\dots

\newscene

Groaning I opened my eyes again and felt for my head then I realized I wasn't in the cave anymore. Waves of dizzyness rushed over me as I tried to turn my head around to see where i was and with an urgh and the realization that I was in one of the camp tents i sank back down. John rushed through the tent flap. "Careful you hit your pretty bad back in that cave." he told me as he knelt beside the makeshift bed i was lying on and touched my hair gingerly. His tocuh was gentle but his eyes looked haunted. 

//TODO: stopping first person writing. i'll have to rewrite the earlier parts

"Wha-what happend in the cave? Gods, wahat was that monster?" stammered Jana as she held her aching head. "Monster?" John looked confused. "Yes that thing with the big black head and the glass eyes." John looked nonplussed and then remembered. "Do you mean this?" and held up a black rubber contraption with two big glass eyes inset a cartridge where the mouth would be. "It's a gas mask we use them when the air is not safe\dots" he fell silent and whispered "like in the cave." He began to shiver and wrapped his arms around him and seemed to forget about her. Jana reached silently out for him and lay her hand on his arm. "What happened in the cave?" she asked. Slowly he began to focus on her again. "I\dots I don't know. We were excavating, trying to find a way deeper when we reached a chamber. We don't know who build it but there was the outline of a door. The others debated how to proceed but the Professor wanted to open it." he shudders and shake his head. "We should never have broken the stone with our pickaxes. There was something like a foul smelling wind coming out of it and Jameson sent me to get the gasmasks for safety but the PRofessor was already sticking his head in the hole. I came back to the camp and after putting one of the masks one went back inside\dots" he bites his lips and stops breathes heavily before he continues. "When I came back to the chamber there was chaos. It was filled waist high with some kind of smoke or fog and there seemed to be somethign moving inside it. The Professor, Jameson and the rest where trying to fight somethig off that had grabbed them by their feet or legs. I panicked and ran\dots" Suddenly he sat upright. "What if it follows me out here? We have to run! We aren't safe." Jana still groggy from her head injury slowly came into a sitting position and everythign swam in front of her. "I don't know if can walk like this John." she said grabbing the bed posts hoping the spinning would stop. "I'll help you but please we must leave before it gets dark and whatever is in that cave tries to follow us" Johnbegged and put her arms around her. Jana slowly stood with his help and together they left the tent. A pitiful pair they were, he scared half to death and she not able to walk straigth properly and wasn't there laughter just at the edge of their hearing?. John looked around haunted and together they started on the path down from the hills.

\newscene

Their progress was slow, John had to guide Jane carefully in her foggy state and the tendrils of fear followed thema nd brushed against their minds constantly. More than once he could barely keep her from loosing her balance when stone got loose beneathe her foot and rolled dowhill.  But the further they got away the better progress they seemed able to make and Jans head was slowly getting clearer again although she had a nasty bump on the back of her head and her blond hair was crusted in blood. And finally they reached the bottom of the hillscape and the grass meadows lay before them dew glistening on the grass. They made better progress now but as the sun sank towards the horizon the temperature fell and the dew turned slowly into mist. Soon their feet began to drag paths of clear air through a thin layer of vapory mists but after w hile the mist got thicker and the only sign of the grass was the whispering sounds it made as their feets glided through it. John gasped as his mind played a trick on him and he thought for a moment that he saw one of the things from the cave sliding through the mists Jana suddenly stopped looking suddenly awake  and stammered. "Mi-ist. Not good\dots. Ghosts." "What do you mean ghosts?" Johna asked as he looked into her eyes. But janas face was vague again, her eyes hidden in the wooly gaze of her head injury. He sighed and took her hand and they started again trhough the sea of mists. Somehow it seemed to him as if after the short stop the mists seemd to hold them back, Its tendrils licking against their legs and keepig them ever so slightly back with each step. He felt the fear that vanished as they reached the grass plans rise again and tried to urge Jana along more quickly. The quicker pace seemed to clear her head again at least slightly. "Children stories" she wispered "monsters in the fog. To scare the children to remain in the village at night." She held Johns hand firmly. "Please don't let me alone." He gulped down his own fear to fight her rising panic and tried to sound confident "Never!" Each grasping the others hand they started tpo run towards the village keeping themselves froms tumbling when one of them misstepped in the mists. And run they did, each one of them seeing somethign move in the corner of their eyes now and then as a feeling of being hunted hung heavily in the air. And was that just the long grass sliding over their feet or was that something slick and slimy just now? Dusk settled and they breathed heavily from exertion as finally the ring of stones around the village came into view. " There we made it." John shoutd happily just as a roar soudned behind them and the slithering soud of something started to close in on them. Jana shrieked and missed a step her foot goind deep into a hole straining her ankle and she splashe down onto the wet ground. John stopped and helped her up again panic in his eys and dragged her towards the stones throwing scared looks behind. Was it just the swirlign mists or have that been tentacles? He slogged with Jana leaning heavily on him towards the stones. Only a short distance remained. They might still make if even though he could almost feel a cold evil breath on his neck.The Stones loomed up before him imonusly, almost like a wall now and his heart jumped with joy. Suddenly somethingmade a cracking sound like a whip behind him and he felt s trong slimy tentacle wrap around his foot. " No! he screamed. He was so close but the tentacle gripped his foot and yanked heavily as he lost his balance. He threw Jana forward and tried to regain his balance as he landed on all fours and was slowly dragged back into the mist. Jana propelled by Johns push stumbled forward passing between the stones before she hit the ground. Dazed with pain and her injuries she fell on the dry and mistfree ground of the village mumbling "We made it John\dots We made it\dots John?!"
